---
title: "Introduction to cvir"
author: "Manus AI"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to cvir}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Introduction

The `cvir` package provides tools for calculating Content Validity Index (CVI) metrics and visualizing expert ratings using `ggplot2`.

## Installation

YouYou can install the development version of `cvir` from GitHub with:

```r
# install.packages("devtools")
devtools::install_github("mscazmy/cvir")
```

## Example Usage

Let's create some sample data to demonstrate the package's functionality. We'll simulate ratings from 5 experts on 10 items, using a 4-point Likert scale (1 = not relevant, 2 = somewhat relevant, 3 = relevant, 4 = highly relevant).

```{r setup}
library(cvir)
library(ggplot2)

# Simulate data
set.seed(123)
ratings_data <- matrix(sample(1:4, 50, replace = TRUE, prob = c(0.1, 0.1, 0.4, 0.4)),
                       nrow = 10, ncol = 5,
                       dimnames = list(paste0("Item_", 1:10), paste0("Expert_", 1:5)))

# Convert to data frame for easier handling if needed, though matrix is fine for core functions
ratings_df <- as.data.frame(ratings_data)
print(ratings_df)
```

### Calculating CVI Metrics

We can calculate Item-level CVI (I-CVI), Scale-level CVI (S-CVI/Ave, S-CVI/UA), and Modified Kappa using the provided functions.

```{r calculations}
icvi_scores <- calc_icvi(ratings_df)
print(icvi_scores)

scvi_ave_score <- calc_scvi_ave(ratings_df)
print(scvi_ave_score)

scvi_ua_score <- calc_scvi_ua(ratings_df)
print(scvi_ua_score)

kappa_scores <- calc_kappa(ratings_df)
print(kappa_scores)

# Or get a summary
cvi_results <- cvi_summary(ratings_df)
print(cvi_results)
```

### Visualizing CVI Scores

The package also includes `ggplot2` based functions for visualizing the results.

```{r plots, fig.width=7, fig.height=5}
plot_icvi(ratings_df)
```

### Visualizing Expert Ratings

To see the individual expert ratings for each item, a heatmap can be generated.

```{r heatmap, fig.width=7, fig.height=7}
plot_ratings(ratings_df)
```
